Estimating Information Transfer in Hard Parameter Sharing via Precise Bias-variance Asymptotics

### 2021-07-17 revision_journal/results.tex
figs for sec 3.3

\begin{figure}[!t]
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=0.8\textwidth]{figures/verify_covariate_shift.eps}
		\caption{Illustrating variance estimates for finite $p$}
		\label{fig_sec3_verify_cov}
	\end{subfigure}
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=0.8\textwidth]{figures/covariate_shift.eps}
		\caption{Sample sizes vs. covariate shift}
		\label{fig_sec3_covariate}
	\end{subfigure}
	\caption{We verify that Theorem \ref{thm_main_RMT} provides incredibly accurate estimates of the empirical variance under various finite sample sizes and dimensions.
	Furthermore, we illustrate an intriguing dichotomy between sample sizes and covariate (cf. Claim \ref{claim_dichotomy}).
	When $n_1 \ge n_2$, the lowest risk for predicting task two's labels is achieved by transferring from a dataset that has the same covariance matrix as task two. 
	When $n_1 < n_2$, the lowest risk is instead achieved by transferring a covariate-shifted dataset.
	Both simulation uses $\sigma = 1/2$.
	Figure \ref{fig_sec3_verify_cov} fixes $\lambda = 4$ and varies $n_1, p$.
	Figure \ref{fig_sec3_covariate} fixes $p = 100, n_2 = 300$ while varying $n_1, \lambda$.}
	\label{fig_sec31}
\end{figure}

@@

>>>>

\begin{figure}[!t]
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=0.8\textwidth]{figures/verify_covariate_shift.eps}
		\caption{Illustrating variance estimates for finite $p$}
		\label{fig_sec3_verify_cov}
	\end{subfigure}
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=0.8\textwidth]{figures/covariate_shift.eps}
		\caption{Varying the covariate shift parameter $\lambda$}
		\label{fig_sec3_covariate}
	\end{subfigure}
	\caption{We verify that Theorem \ref{thm_main_RMT} provides incredibly accurate estimates of the empirical variance under various finite sample sizes and dimensions.
	Furthermore, we illustrate an intriguing dichotomy between sample sizes and covariate (cf. Claim \ref{claim_dichotomy}).
	When $n_1 \ge n_2$, the lowest risk for predicting task two's labels is achieved by transferring from a dataset that has the same covariance matrix as task two. 
	When $n_1 < n_2$, the lowest risk is instead achieved by transferring a covariate-shifted dataset.
	Both simulation uses $\sigma = 1/2$.
	Figure \ref{fig_sec3_verify_cov} fixes $\lambda = 4$ and varies $n_1, p$.
	Figure \ref{fig_sec3_covariate} fixes $p = 100, n_2 = 300$ while varying $n_1, \lambda$.}
	\label{fig_sec31}
\end{figure}

@@

\begin{figure}[!t]
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=0.8\textwidth]{figures/covariate_and_model_shift_a.eps}
		\caption{Varying sample size under covariate shift}
		\label{fig_sec3_cov_mo_a}
	\end{subfigure}
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=0.8\textwidth]{figures/covariate_and_model_shift_b.eps}
		\caption{Varying sample size under model shift}
		\label{fig_sec3_cov_mo_b}
	\end{subfigure}
	\caption{We further show that our observations in Figures \ref{fig_sec31} and \ref{fig_sec3_model_shift} extend to settings with both covariate and model shift.
	Both simulation use $p = 100, n_2 = 300, \sigma = 1/2$.
	Figure \ref{fig_sec3_cov_mo_a} fixes $\mu = 0.1$ while varying $\lambda, n_1$.
	Figure \ref{fig_sec3_cov_mo_b} fixes $\lambda = 4$ while varying $\mu, n_1$.}
	\label{fig_sec33}
\end{figure}
